---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r echo=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)

library(dplyr)
library(magrittr)
library(taxize)
library(stringr)
library(knitr)
library(taxizehelper)
```

# taxizehelper: Convenience functions for the `taxize` package.

## What is `taxizehelper`?

`taxizehelper` is a personal package that helps me use rOpenSci's [`taxize`](https://ropensci.org/tutorials/taxize_tutorial/) package more succinctly. `taxize` helps you retrieve up-to-date taxonomic information, so you can easily do things like:

1. Ensure that you're referring to species by their current names.
2. Error-check and repair a list of misspelled names.
3. Retrieve taxonomic ranks (order, class, family etc.) for names.
4. Discover the authorities who named your species.


## Project participants

- Desi Quintans (https://twitter.com/eco_desi)

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.


## Installation

```{r install, echo=TRUE, eval=FALSE}
install.packages("devtools")
devtools::install_github("DesiQuintans/taxizehelper")
library(taxizehelper)
```

`taxizehelper` currently has only one function:

1. `search_gnr(species_list)` --- Get taxonomic info for a list of taxa in a tidy dataframe.

## Ex. 1: Use `search_gnr()` to get a dataframe of taxonomic ranks

```{r}
# A list of insect species recorded within 1 km of my university.
data("wsu_hwk_insects")
print(wsu_hwk_insects)

output <- search_gnr(wsu_hwk_insects) 

class(output) 

glimpse(output, width = 85)
```

The ICN ranks are ordered so that you can access them with `kingdom:genus`.
